The CrypTool Script: \\ Cryptography, Mathematics and More \\ \vspace{30pt} {\large Background reading\\%*[-8pt] for the free e-learning program CrypTool\\ (10th edition -- distributed with CrypTool version 1.4.30)} \vspace{60pt}

### 2012-07-22 script/en/chapters/aboutcryptool.tex
QA
fixed warnings
readme: minor update // script: update of overview, preface, introduction, appendices for function overviews of CT2 and JCT

% --------------------------------------------------------------------------
\clearpage\phantomsection
\addcontentsline{toc}{chapter}{Overview}
\chapter*{Overview about the Content of the CrypTool Script}

@@

Big parts of this script are dedicated to the fascinating topic of 
{\bf prime numbers} (chap. \ref{Label_Kapitel_2}).
%\hyperlink{Kapitel_2}{{\bf prime numbers}}. 
Using numerous examples,
{\bf modular arithmetic} and 
{\bf elementary number theory} (chap. \ref{Chapter_ElementaryNT})
are introduced and applied in an exemplary manner for the {\bf RSA procedure}.

@@

Chapter \ref{Chapter_EllipticCurves} describes {\bf elliptic curves}:
they could be used as an alternative to RSA and in addition are extremely
well suited for implementation on smartcards.

The \hyperlink{Chapter_Crypto2020}{last chapter} {\bf Crypto2020}
discusses threats for existing cryptographic methods and introduces
alternative research approaches to achieve long-term security
of cryptographic schemes.

Whereas the \textit{e-learning program} CrypTool\index{CrypTool} motivates and
teaches you how to use cryptography in practice, the \textit{script} provides
those interested in the subject with a deeper understanding of the mathematical
algorithms used -- trying to do it in an instructive way.
If you are already a little bit familiar with this field of knowledge you can
gain a fast overview about the functions delivered by CrypTool looking at the
{\bf menu tree} (see appendix \ref{s:appendix-menutree}).

>>>>

% --------------------------------------------------------------------------
% HACK to fix warning "destination with the same identifier .. has already been used, ...":
\makeatletter \renewcommand{\thepage}{~\csname @roman\endcsname \c@page~} \makeatother
\clearpage\phantomsection
% HACK to fix warning "destination with the same identifier .. has already been used, ...":
\makeatletter \renewcommand{\thepage}{\csname @roman\endcsname \c@page} \makeatother
\addcontentsline{toc}{chapter}{Overview}
\chapter*{Overview about the Content of the CrypTool Script}

@@

Big parts of this script are dedicated to the fascinating topic of 
{\bf prime numbers} (chap. \ref{Label_Kapitel_Primes}).
%\hyperlink{Kapitel_2}{{\bf prime numbers}}. 
Using numerous examples,
{\bf modular arithmetic} and 
{\bf elementary number theory} (chap. \ref{Chapter_ElementaryNT})
are introduced and applied in an exemplary manner for the {\bf RSA procedure}.

@@

Chapter \ref{Chapter_EllipticCurves} describes {\bf elliptic curves}:
They could be used as an alternative to RSA and in addition are extremely
well suited for implementation on smartcards.

The \hyperlink{Chapter_Crypto2020}{last chapter} {\bf Crypto2020}
discusses threats for currently used cryptographic methods and introduces
alternative research approaches to achieve long-term security
of cryptographic schemes.

Whereas the \textit{e-learning program} CrypTool\index{CrypTool} motivates and
teaches you how to use cryptography in practice, the \textit{script} provides
those interested in the subject with a deeper understanding of the mathematical
algorithms used -- trying to do it in an instructive way.
If you are already a little bit familiar with this field of knowledge you can
gain a fast overview about the functions delivered by the different CrypTool
variants looking at the {\bf menu trees} (see appendix \ref{s:appendix-menu-overview-CT1} etc.).
